On Secure Delegation of SampBQP with a Classical Client

### 2019-12-23 qpip.tex
Fix grammatical mistake
Fix typo

	With these parameters, we claim that \hyperref[ProtoQPIP1]{Protocol~\ref*{ProtoQPIP1}} does what is required.
	\floatname{algorithm}{Protocol}
	\begin{algorithm}
		\caption{Our $\QPIP_1$ protocol}
		\label{ProtoQPIP1}
		\begin{algorithmic}[1]
			\State The honest prover sends $N$ identical copies of $\ket{\psi_{C'(x)}}$, where $C'$ is $C$ padded with identities as mentioned in \hyperref[idpadding]{Observation~\ref*{idpadding}}
			\State The verifier randomly picks $m$ copies for outputting and $n$ copies for checking
			\State $c\gets0$
			\State $y\gets$null
			\For{$i\gets1, N$}
			    \If{Copy is for checking}
				\State The verifier runs \autoref{AlgGroundStateCheck} as described by \hyperref[ProtoGroundStateCheck]{Observation~\ref*{ProtoGroundStateCheck}}.
			    \If{Test passes}
			        $c\gets c+1$
			    \EndIf
			    \ElsIf{Copy is for outputting}
			    \State The verifier measures the copy in standard basis
			    \If{measurement result of the clock register $\geq\frac{T}{2}$}
			        \If{$y=$null}
			            $y\gets$ measurement result of the data register
                    \EndIf
			    \EndIf
			    \Else
			    \State The verifier measures the entire register in standard basis
			    \EndIf
			\EndFor
			\If{$\frac{c}{n}\geq\frac{1}{2}-\varepsilon$}
			\If{$y\ne$null}
			\State output $y$
			\Else
			\State Reject
			\EndIf
			\Else
			\State Reject
			\EndIf
		\end{algorithmic}
	\end{algorithm}

@@

	Such $\rho_i$ are $O(\negl(\varepsilon))$-close to $\ket{\psi_{C(x)}}$, by applying a Chernoff bound to \autoref{ThmXZCheck}.

>>>>

	With these parameters, we claim that \hyperref[ProtoQPIP1]{Protocol~\ref*{ProtoQPIP1}} does what is required.
	\floatname{algorithm}{Protocol}
	\begin{algorithm}
		\caption{Our $\QPIP_1$ protocol}
		\label{ProtoQPIP1}
		\begin{algorithmic}[1]
			\State The honest prover sends $N$ identical copies of $\ket{\psi_{C'(x)}}$, where $C'$ is $C$ padded with identities as mentioned in \hyperref[idpadding]{Observation~\ref*{idpadding}}
			\State The verifier randomly picks $m$ copies for outputting and $n$ copies for checking
			\State $c\gets0$
			\State $y\gets$null
			\For{$i\gets1, N$}
			    \If{Copy is for checking}
				\State The verifier runs \autoref{AlgGroundStateCheck} as described by \hyperref[ProtoGroundStateCheck]{Observation~\ref*{ProtoGroundStateCheck}}.
			    \If{Test passes}
			        $c\gets c+1$
			    \EndIf
			    \ElsIf{Copy is for outputting}
			    \State The verifier measures the copy in standard basis
			    \If{measurement result of the clock register $\geq\frac{T}{2}$}
			        \If{$y=$null}
			            \State $y\gets$ measurement result of the data register
                    \EndIf
			    \EndIf
			    \Else
			    \State The verifier measures the entire register in standard basis
			    \EndIf
			\EndFor
			\If{$\frac{c}{n}\geq\frac{1}{2}-\varepsilon$}
			\If{$y\ne$null}
			\State output $y$
			\Else
			\State Reject
			\EndIf
			\Else
			\State Reject
			\EndIf
		\end{algorithmic}
	\end{algorithm}

@@

	Such $\rho_i$ is $O(\negl(\varepsilon))$-close to $\ket{\psi_{C(x)}}$, by applying a Chernoff bound to \autoref{ThmXZCheck}.
